%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Muhammad}{Saad}{ \urlstyle{same}\href{https://www.linkedin.com/in/muhammad-saad-ms}{linkedin/muhammad-saad-ms}   |   \href{https://github.com/MuhammadSaad20}{github/MuhammadSaad20}\\
                          +92 323 2978 188 | \href{mailto:msaad12199@gmail.com}{msaad12199@gmail.com
}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{FAST NUCES}
\descript{BS in Computer Science}
\location{July 2021| Karachi, Pakistan}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Languages  }
\location{}
Java  \textbullet{} Python \textbullet{} JavaScript \\
HTML / CSS  \textbullet{} SQL  \\ 
\vspace{0.3 em}
\subsection{Frameworks }
\location{}
Selenium \textbullet{} TestNG \textbullet{} Appium \\
Cucumber  (BDD)  \textbullet{} PyUnit (TDD)  \\
\vspace{0.3 em}
\subsection{Testing Skills}
\location{}
\textbullet{} \textbf{Manual Testing} (Functional, Regression, UAT, Smoke, Sanity Testing)\\
\vspace{0.2 em}
\textbullet{} \textbf{Test Automation} (UI and API testing) \\
\vspace{0.2 em}
\textbullet{} \textbf{CI/CD Pipelines} (Jenkins, Azure DevOps) \\
\vspace{0.2 em}
\textbullet{} \textbf{Agile Methodologies} (Scrum, Sprint Planning) \\
\vspace{0.2 em}
\textbullet{} \textbf{Database Testing} (SQL, PostgreSQL, NoSQL) \\
\vspace{0.2 em}
\textbullet{} \textbf{API Testing} (Postman) \\
\vspace{0.2 em}
\textbullet{} \textbf{Problem Solving} (Troubleshooting, Debugging) \\
\vspace{0.2 em}
\textbullet{} \textbf{Generative AI}\textbf{ (}GPT, T5, LLaMa, Codex\textbf{ )} \\
\vspace{0.2 em}
\textbullet{} \textbf{Performance Testing}: JMeter, K6\\
\vspace{0.3 em}
\subsection{Developer  Tools}
\location{}
Git \textbullet{} Docker \textbullet{} AWS \\
Nginx \textbullet{}  Putty \textbullet{} Fiddler  \\
VS Code \textbullet{}  Visual Studio \textbullet{} Intelij  \\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Achievements}
\subsection{Certification  }
\location{}
 \textbullet{} ISTQB Certified Tester {\scriptsize 24-CTFL4-1313-PK} \\
 \vspace{0.1 em}
\textbullet{}  Selenium Web driver Framework \\
\vspace{0.1 em}
\subsection{Awards }
\location{}
  \textbullet{} Departmental Innovation Award  {\scriptsize '24}\\
  \vspace{0.1 em}
\textbullet{}  Departmental Star Performer Award {\scriptsize '23}\\
\vspace{0.1 em}
\textbullet{}  Github Arctic Code Vault Contributor {\scriptsize '20}\\
\vspace{0.1 em}

\subsection{Research Paper }
\location{}
 \textbullet{} Published research paper on \href{https://ieeexplore.ieee.org/document/10099364}{Real-Time Object Detection} at the 4th \href{https://www.ieee.org/conferences/index.html}{iCoMET} {\scriptsize '23}\\ 
 \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Interests}
\location{}
 \textbullet{}  Exploring New Technologies \\
\textbullet{}   Healthy Eating and Fitness  \\
\textbullet{}   Knowledge sharing and mentorship\\
 \sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Astera Software}
\descript{| Senior QA Engineer }
\location{ June 2021 - Present | Hybrid, Westlake Village, CA , USA | Karachi , Pakistan}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Engineered \textbf{API flow automation} and implemented \textbf{regression testing} within the \textbf{CI/CD pipeline}, achieving a \textbf{90\% reduction in test execution time} and expediting testing cycles to support \textbf{faster releases}.
\item Developed and executed \textbf{300+ manual and automated test cases}, achieving \textbf{~90\% test coverage} to meet requirements and ensure product quality.
  \item Conducted \textbf{functional, non-functional}, and exploratory testing, ensuring \textbf{100\%} requirement validation and \textbf{99\%} feature reliability.
\item Developed and implemented an \textbf{end-to-end automation framework} for UI testing, \textbf{cutting manual effort by 50\%} and improving test cycle efficiency.
     \item Established baseline regression testing for API, data pipelines, and EDI systems, ensuring \textbf{90\% } product stability.
     \item Performed \textbf{performance and API testing} for multi-tenant architecture, ensuring \textbf{90\%-95\%} (approx) system up time and seamless integration.
    \item Optimized testing environments with \textbf{Dockerized containers}, improving server utilization by \textbf{200\%}.
    \item Authored \textbf{1000+} test plans, scenarios, and defect reports, ensuring \textbf{100\%} alignment with business goals.
\item Leveraged \textbf{Generative AI} models for automated test data generation and optimization of test cases, reducing manual effort.
    \item Resolved \textbf{100+ customer-reported issues} by debugging and collaborating with cross-functional teams to enhance system reliability.
    \item Refactored \textbf{ETL solutions} for 20+ customers, improving processing times and efficiency.
\item Conducted monthly knowledge-sharing sessions for 10+ team members on \textbf{CI/CD}, and \textbf{regression testing automation}.
  \item Configured backend proxy servers to enhance API isolation by \textbf{50\%}, optimizing performance for customer proof-of-concept (POC) environments.
\end{tightemize}
\sectionsep

\runsubsection{TripleK Technologies}
\descript{| Associate Software Engineer    }
\location{April 2021 – June 2021 |  Remote, Pakistan}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
 \item Integrated cloud provider API, enhancing application functionality.
\item Improved stakeholder communication, optimizing the hiring process and increasing engineering hires.
\end{tightemize}
\sectionsep

\runsubsection{WebNetik (Pvt) Ltd }
\descript{| Software Developer Intern   }
\location{July 2020 – Aug 2020 | Remote, Pakistan}
\begin{tightemize}
 \item Integrated a calendar plugin to enhance scheduling and event management.
 \item Streamlined deployment processes, reducing downtime and improving performance.
\end{tightemize}
\sectionsep

\section{Projects}
\vspace{1.5 em} % Adjust the value (e.g., 0.5em or 1em) to set the desired vertical spacing.
\begin{tightemize}
\item \textbf{\href{https://github.com/SafeDrive120}{Safe Drive}}: Developed a mobile application for collision prediction and real-time warning systems, enhancing road safety.
\item \textbf{\href{https://github.com/MuhammadSaad20/FoodAIN}{Food AI}}: Created a desktop application for local food image recognition and AI-powered meal recommendations.
\item \textbf{\href{https://github.com/MuhammadSaad20/SAVESLIFE/tree/master}{Saves Life}}: Designed a web-based blood donation platform, streamlining client-donor connections for better blood availability.
\end{tightemize}
\sectionsep
\end{minipage} 
\end{document}  \documentclass[]{article}
